% !TEX root = nanograv_11yr_cw.tex
The NANOGrav project receives support from National Science Foundation (NSF) Physics Frontier Center award \#1430284.
NANOGrav research at UBC is supported by an NSERC Discovery Grant and Discovery Accelerator Supplement and by the Canadian Institute for Advanced Research.
M.V.\ and J.S.\ acknowledge support from the JPL RTD program.
S.R.T.\ was partially supported by an appointment to the NASA Postdoctoral Program at the Jet Propulsion Laboratory, administered by Oak Ridge Associated Universities through a contract with NASA.
J.A.E.\ was partially supported by NASA through Einstein Fellowship grants PF4-150120.
% P.T.B. acknowledges support from the West Virginia University Center for Gravitational Waves and Cosmology.
% S.B.S. and C.A.W. were supported by NSF award \#1815664.
% W.W.Z. is supported by the Chinese Academy of Science Pioneer Hundred Talents Program, the Strategic Priority Research Program of the Chinese Academy of Sciences grant No.~XDB23000000, the National Natural Science Foundation of China grant No.~11690024, and by the Astronomical Big Data Joint Research Center, co-founded by the National Astronomical Observatories, Chinese Academy of Sciences and the Alibaba Cloud.
Portions of this work performed at NRL are supported by the Chief of Naval Research.
The Flatiron Institute is supported by the Simons Foundation.
Portions of this research were carried out at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration.
\par

This work was supported in part by National Science Foundation Grant PHYS-1066293 and by the hospitality of the Aspen Center for Physics.
We are grateful for computational resources provided by the Leonard E.\ Parker Center for Gravitation, Cosmology and Astrophysics at the University of Wisconsin-Milwaukee, which is supported by NSF Grants 0923409 and 1626190.
Data for this project were collected using the facilities of the Green Bank Observatory and the Arecibo Observatory.
The National Radio Astronomy Observatory and Green Bank Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.
The Arecibo Observatory is a facility of the National Science Foundation operated under cooperative agreement by the University of Central Florida in alliance with Yang Enterprises, Inc.\ and Universidad Metropolitana.
Copyright 2019.
